\documentclass[margin,line]{res}
%\usepackage{pdfsync}
\usepackage[colorlinks=true, linkcolor=black,citecolor=black,
urlcolor=black]{hyperref}
%\usepackage{pdfsync}
\oddsidemargin -.5in
\evensidemargin -.6in
\textwidth=6.1in
\itemsep=0in
\parsep=0in
\setlength{\textheight}{9.7in}
\topmargin -0.4in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}
\name{Jong-Han Kim}

\begin{resume}

\section{\sc Contact Information}
Agency for Defense Development \hfill
{\texttt{jonghank@add.re.kr}} \hspace{0.9mm} (official)\\
160, Bugyuseong-daero 488beon-gil, Yuseong-gu, 	\hfill {\texttt{tojhkim@gmail.com}} (preferred)\\
Daejeon, South Korea, 34060 \hfill +82-10-9056-2543

\section{\sc Education}
\textbf{Stanford University} \hfill 2012.6 \\
Ph.D. in Aeronautics and Astronautics \\
\emph{Information Systems Lab.} \hfill Advisor: Prof. Sanjay Lall \\
Dissertation: \emph{Separable problems in optimal cooperative control of networked systems }
%\\ \phantom{.} \hfill 
(Dissertation advisors: Prof. Sanjay Lall, Prof. Stephen Boyd, Prof. Stephen Rock)

\textbf{Korea Advanced Institute of Science and Technology (KAIST)} \hfill
2001.2 \\ 
M.S. in Aerospace Engineering\\ 
\emph{Flight Dynamics and Control Lab.} \hfill Advisor: Prof. Min-Jea Tahk \\
Dissertation: \emph{An accelerated co-evolutionary algorithm and its application to attitude control design of flexible satellites}

\textbf{Korea Advanced Institute of Science and Technology (KAIST)} \hfill
1999.2 \\ 
B.S. in Aerospace Engineering 

\section{\sc{Work \ \ Experience}}

\textbf{Agency for Defense Development (ADD)} \hfill {Researcher / Senior researcher} \\
Daejeon, South Korea \hfill {2001.1 - present} \\
\emph{Guidance systems R\&D directorate}

\textbf{United Technologies Research Center (UTRC)} \hfill {Summer intern} \\
East Hartford, CT, USA \hfill {2007.7 - 2007.9} \\
\emph{Systems division}

\textbf{Satellite Technology Research Center (SaTReC), KAIST} \hfill {Intern}
\\ 
Daejeon, South Korea \hfill {2000.1 - 2001.1} \\
\emph{Attitude determination and control group}

\section{\sc{Honors and Awards}}

\textbf{Ministerial Commendation, Minister of National Defense} \hfill{2017.8} \\
Cited for pivotal roles in applying machine learning and convex optimization techniques for developing cutting-edge missile guidance systems. 

\textbf{Outstanding Young Researcher Award, ICROS} \hfill {2017.5} \\
Given to outstanding young researchers under 40 with notable research achievements, by the Institute of Control, Robotics and Systems (ICROS).

\section{\sc{Research Experience}}

\textbf{Machine learning based intelligent guidance techniques}
\hfill \emph{ADD}\\%\footnote{Works stated under `ADD' category are all beyond lab-level works.}} \\
Online $\ell_1$-regularized optimization for optical misalignment cancellation of strap down seekers. \\ 
Target shape identification using RF signals based on unsupervised learning.

\textbf{Integrated guidance and control for constrained precision homing}
\hfill \emph{ADD} \\
Finite horizon integrated guidance and control for constrained terminal homing of high performance missile systems.

\textbf{Guidance and control designs for full-scale missile development programs}
\hfill \emph{ADD} \\
Highly reliable guidance and control design/implementation for several state-of-the-art missile systems development programs. The works include classical, optimal, or robust control for highly unstable airframes and high-fidelity flight simulation techniques.

\textbf{Optimal decentralized control for large-scale networked systems}
\hfill \emph{Stanford} \\
Theoretical studies on optimal decentralized control using convex analysis and convex optimization. Characterizes convex problems and explicitly solvable problems in optimal control of networked systems under information constraints.

\textbf{Decentralized control for jet engine systems}
\hfill \emph{Stanford} \\
Suboptimal decentralized $H_2/H_{\infty}$ control synthesis.
Convex relaxation and convex approximation of nonconvex optimal control problems. 
Application to jet engine control systems.

%\textbf{Team decision problems, decentralized detection}
%\hfill \emph{Stanford} \\
%Decentralized detection/classification problems relaxed to linear programming
%(LP) or semidefinite programming (SDP). Integer programming.

\textbf{Multiscale/stochastic consensus for decentralized estimation}
\hfill \emph{Stanford / UTRC} \\
Multiscale concepts to applied to consensus problems, for scalable distributed
estimation. Stochastic message passing for convergence acceleration. 
Application to decentralized estimation problems.

\textbf{Tactical missile systems integration}
\hfill \emph{ADD} \\
Mission profile design, operational performance/effectiveness analysis. Flight
performance analysis. Engineering level 6-DOF flight dynamics simulation. 

\textbf{Attitude control for small satellites}
\hfill \emph{SaTReC} \\
Design and experiments for attitude control of flexible satellites. Satellite
bus development for STSAT-1 program. Developing ground test modules.

\textbf{Co-evolutionary algorithms for constrained optimization}
\hfill \emph{KAIST} \\
Constrained optimization, minimax optimization using evolutionary computation.
Applications to design problems or control problems. Convergence
acceleration by using artificial neural networks.

\section{\sc{Selected Publications}}

%{\bf $\bullet$ DISSERTATIONS}
%
%{\bf J.-H. Kim}, \emph{Separable problems in optimal cooperative control of networked systems,} Ph.D. Dissertation, Stanford University, June 2012.
%
%{\bf J.-H. Kim}, \emph{An accelerated co-evolutionary algorithm and its application to attitude control design of flexible satellites,} M.S. Dissertation, KAIST, Feb. 2001.

{\bf $\bullet$ {INTERNATIONAL JOURNALS}}

{\bf J.-H. Kim} and S. Lall, ``Explicit solutions to separable problems in optimal cooperative control,'' \emph{IEEE Transactions on Automatic Control,} vol.60, no.5, pp.1304-1319, 2015. [IF: 4.270]

{\bf J.-H. Kim}, I.H. Whang, and B.M. Kim, ``Finite horizon integrated guidance and control for terminal homing in vertical plane,'' \emph{AIAA Journal of Guidance, Control, and Dynamics,} vol.39, no.5, pp.1104-1112, 2016. [IF: 1.856]

{\bf J.-H. Kim} and I.H. Whang, ``Augmented three-loop autopilot structure based on mixed sensitivity $H_\infty$ optimization,'' \emph{AIAA Journal of Guidance, Control, and Dynamics,} 2017. (Published online with DOI \texttt{https://doi.org/10.2514/1.G003119}) [IF: 1.856]

T.H. Kim, {\bf J.-H. Kim}, and P.S. Kim, ``New guidance filter structure for homing missiles with strapdown IIR seeker,'' \emph{(accepted to) International Journal of Aeronautical and Space Sciences,} 2017. 

{\bf J.-H. Kim}, Y. Han, and I.H. Whang, ``Online $l_1$-regularized optimization for optical misalignment cancellation of strap down seekers,'' \emph{(submitted to) Mathematical Problems in Engineering,} 2017. 

{\bf J.-H. Kim} and M.-J. Tahk, ``Accelerated co-evolutionary algorithms,'' \emph{International Journal of Aeronautical and Space Sciences,} vol.3, no.1, pp.50--60, May 2002.

{\bf $\bullet$ INTERNATIONAL CONFERENCES}

D. Lee, {\bf J.-H. Kim}, and H.-L. Choi, ``Closed-form cooperative guidance law for two missiles with coupled terminal velocity constraints,'' in \emph{Proc. 30th Congress of the International Council of the Aeronautical Sciences,} Sep. 2016.

{\bf J.-H. Kim}, S. Lall, and C.-K. Ryoo, ``Optimal cooperative control of dynamically decoupled systems,'' in \emph{Proc. 51st IEEE Conference on Decision and Control,} pp.4852-4857, Dec. 2012.

{\bf J.-H. Kim} and S. Lall, ``Separable optimal cooperative control problems,'' in \emph{Proc. 2012 American Control Conference,} pp.5868-5873, June 2012.

{\bf J.-H. Kim} and S. Lall, ``A unifying condition for separable two player optimal control problems,'' in \emph{Proc. 50th IEEE Conference on Decision and Control,} pp.3818-3823, Dec. 2011.

{\bf J.-H. Kim}, S. Lall, W. Merrill, and A. Behbahani, ``A computational approach for decentralized control of turbine engines,'' in \emph{Proc. 49th IEEE Conference on Decision and Control,} pp.346-351, Dec. 2010.

W. Merrill, {\bf J.-H. Kim}, S. Lall, S. Majerus, D. Howe, and A. Behbahani, ``Distributed engine control design considerations,'' in \emph{Proc. 46th AIAA/ASME/SAE/ASEE Joint Propulsion Conference \& Exhibit,} July 2010.

{\bf J.-H. Kim}, M. West, S. Lall, E. Scholte, and A. Banaszuk, ``Stochastic multiscale approaches to consensus problems,'' in \emph{Proc. 47th IEEE Conference on Decision and Control,} pp.5551-5557, Dec. 2008.

{\bf J.-H. Kim}, M. West, E. Scholte, and S. Narayanan, ``Multiscale consensus for decentralized estimation and its application to building systems,'' in \emph{Proc. 2008 American Control Conference,} pp.888-893, June 2008.

{\bf J.-H. Kim}, C.-S. Park, and M.-J. Tahk, ``An accelerated co-evolutionary algorithm using neural networks,'' in \emph{Proc. 37th JSASS Aircraft Symposium,} Tokyo, Japan, Oct. 1999.

{\bf $\bullet$ PATENTS}

{\bf J.-H. Kim}, I.H. Whang, B.M. Kim, and H.R. Park, \emph{Terminal homing method for flight vehicle and apparatus thereof}, KR Patent KR101602311B1, issued March 10, 2016.

T.H. Kim and {\bf J.-H. Kim}, \emph{Guidance filter model for relative kinematic estimation using two-axes gimbaled RF seeker}, (pending).

{\bf $\bullet$ DOMESTIC JOURNALS}

{\bf J.-H. Kim}, Y. Han, and I.H. Whang, ``Optical misalignment cancellation via online $l_1$ optimization,'' \emph{Transactions of the Korean Institute of Electrical Engineers,} vol.66, no. 7, pp.1078--1082, July 2017.

{\bf J.-H. Kim}, T.-H. Kim, and B.-E. Jun, ``Target shape identification based on unsupervised learning,'' \emph{(submitted to) Journal of Institute of Control, Robotics and Systems.}

C.-K. Ryoo, M.-J. Tahk, and {\bf J.-H. Kim}, ``Trajectory optimization and guidance of terminal velocity constrained missiles,'' \emph{Journal of the Korean Society for Aeronautical \& Space Sciences,} vol.32, no.6, pp.72-80, Aug. 2004.

H.-W. Lee, {\bf J.-H. Kim}, M.-J. Tahk, and D.-J. Park, ``Verification and validation of attitude control subsystems of KITSAT series satellites,'' \emph{ICASE Magazine,} vol.6, no.5, pp.31--37, Sep. 2000.

{\bf $\bullet$ DOMESTIC CONFERENCES}

B.M. Kim, H.-S. Kim, {\bf J.-H. Kim}, and I.H. Whang, ``Adaptive controller for the uniformization of time response,'' in \emph{Proc. 2017 KIEE Summer Conference,} pp.1422-1423, July 2017.

I.H. Whang, H.R. Park, B.M. Kim, {\bf J.-H. Kim}, and H.-S. Kim ``Optimal initialization for roll controller,'' in \emph{Proc. 2017 KIEE Summer Conference,} pp.1420-1421, July 2017.

I.H. Whang, H.R. Park, B.M. Kim, and {\bf J.-H. Kim}, ``Optimal initiation for 3-loop roll regulator,'' in \emph{Proc. 32nd ICROS Annual Conference,} pp.95-96, May 2017.

I.S. Kim, {\bf J.-H. Kim}, and H.-L. Choi ``Nonclassical Optimal guidance laws based on nonclassical penalty functions,'' in \emph{Proc. 2017 KSAS Spring Conference,} pp.242-243, April 2017.

I.H. Whang, {\bf J.-H. Kim}, B.M. Kim, and H.R. Park, ``Statistical decision making for random fault correction,'' in \emph{Proc. 2016 KIEE Summer Conference,} pp.1450-1451, July 2016.

B.M. Kim, {\bf J.-H. Kim}, D.K. Sang, and I.H. Whang, ``Performance comparison of the PI roll attitude controller and the 3-loop roll attitude controller,'' in \emph{Proc. 2014 KSAS Autumn Conference,} pp.1414--1417, Nov. 2014.

I.H. Whang, {\bf J.-H. Kim}, and B.M. Kim, ``A study on performance degradation due to measurement mismatches,'' in \emph{Proc. 2014 KIEE Summer Conference,} pp.1482-1483, July 2014.

{\bf J.-H. Kim}, I.H. Whang, and B.M. Kim, ``Finite horizon integrated guidance and control for terminal homing,'' in \emph{Proc. 2013 Conference on Information and Control Systems,} pp.135-136, Oct. 2013.

I.H. Whang, S.J. Kim, {\bf J.-H. Kim}, and B.M. Kim, ``Speed-height target curve following controller design,'' in \emph{Proc. 2013 Conference on Information and Control Systems,} pp.131-132, Oct. 2013.

B.M. Kim, I.H. Whang, and {\bf J.-H. Kim}, ``Mixed aerodynamic and thrust vector control design using the dual PCH logic,'' in \emph{Proc. 2013 Conference on Information and Control Systems,} pp.129-130, Oct. 2013.

I.H. Whang, B.M. Kim, and {\bf J.-H. Kim}, ``Terminal guidance design using adaptive biased proportional navigation law,'' in \emph{Proc. 2013 KIEE Summer Conference,} pp.1639-1630, July 2013.

{\bf J.-H. Kim}, S. Lall, and C.-K. Ryoo, ``Optimal salvo guidance under fixed communication topology,'' in \emph{Proc. 16th Missile Systems Conference,} Oct. 2012. 

K.-R. Choi, {\bf J.-H. Kim}, J.-Y. Ahn, and M.-J. Tahk, ``Controller design by using CEALM optimization  techniques,'' in \emph{Proc. 11th Missile Systems Conference,} Oct. 2001.

\end{resume}
\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
